On $R$-models

### 2019-04-07 PaperDraft.tex
prove p-morphism lemma explicitly
updates in notation and defs

\theoremstyle{col}
\newtheorem{col}{Corollary}
\usepackage{listings} 		% for source code
\date{}
\author[1,2]{Daniel Rogozin}
\affil[1]{Lomonosov Moscow State University}
\affil[2]{Serokell O\"{U}}
\title{Models of Lambek calculus enriched with subexponentials}

@@

  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | {!_s \mathcal{F}_{\Sigma}}_{s \in \mathcal{I}} $
\end{defin}

@@

\begin{defin}
  By ${L^{*}_{\bf 1} \land \lor}_{\bf S4}$ we mean $SMALC_{\Sigma}$, where $\Sigma = \{ s \}$ and $C = W = E = \emptyset$.
\end{defin}

@@

Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and $\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of $\mathcal{Q}_2$.

@@

\begin{proof}
  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$.

  Let $a_i \in S$ for each $i \in I$, so $\bigvee \limits_{i \in I} a_i \in S$, but $f(a_i) \in f(\mathcal{S})$ for any $i \in I$,
  so $f(\bigvee \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} (f (a)) \in f(\mathcal{S})$, so $f(\mathcal{S})$ is closed under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
\end{proof}

@@

\begin{lemma}
  $\Box_1 a_1 \cdot \Box_2 a_2 \leq \Box^{'} (\Box_1 a_1 \cdot \Box_2 a_2)$, where $\Box_i \leq \Box, i = 1,2$.
\end{lemma}

@@

\begin{defin}
$ $
\begin{enumerate}
  \item An open modality is called central, if for all
  $a, b \in \mathcal{Q}, \Box(a) \cdot b = b \cdot \Box(a)$.

@@

  $\begin{array}{lll}
  & b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Right weak square-increase}& \\
  &\Box a \cdot b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Unitality}& \\
  & \Box a \cdot b \cdot e \leq & \\
  & \:\:\:\: \text{Identity}& \\
  &\Box a \cdot b \leq & \\
  & \:\:\:\: \text{Left weak square-increase}& \\
  &\Box a \cdot b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Unitality}& \\
  &e \cdot b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Identity}& \\
  &b \cdot \Box(a)&
  \end{array}$

@@

  Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale,
  then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that $\Box(a) = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
\end{prop}

\begin{proof}
  See
\end{proof}

@@

\begin{enumerate}
  \item $\Box_z (a) = \bigvee \{ s \in S \: | s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \}$;
  \item $\Box_{\mathds{1}} (a) = \bigvee \{ s \in S \: | s \leq a, s \leq \mathds{1} \}$;
  \item $\Box_{idem} (a) = \bigvee \{ s \in S \: | s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$;
  \item $\Box_{z, \mathds{1}}, I_{z, idem}, I_{\mathds{1}, idem}, I_{z, \mathds{1}, idem}$.
\end{enumerate}
\end{prop}

@@

\begin{prop}
  $\bigvee S$ is an ideal.
\end{prop}

\begin{lemma}
  $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$.
\end{lemma}

Let $A \in Fm$. Then $\{ B \: | \: B \rightarrow A', A' \in A \} \subseteq \bigvee \{ A \}$,
so far as $\bigvee A$ is an ideal.

On the other hand, $\{ B \: | \: B \rightarrow A \}$ is an ideal, it is easy to see that this set is closed under $\lor$.
So, $\bigvee A \subseteq \{ B \: | \: B \rightarrow A \}$.
\end{proof}

\begin{lemma}
  $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$.
\end{lemma}

\begin{proof}
  Let $\bigvee \{ A \} \subseteq \bigvee \{ B \}$,
  then $\{ C | C \rightarrow A \} \subseteq \{ D \: | \: D \rightarrow B \}$.

Thus, $A \in \{ C | C \rightarrow A \}$,
then $A \in \{ D \: | \: D \rightarrow B \}$, hence $A \rightarrow B$.

On the other hand, let $A \rightarrow B$ and $C \in \bigvee \{ A \}$.

Thus, $C \rightarrow A$, then $C \rightarrow B$ by cut.

\begin{lemma}
  Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a quantale.
\end{lemma}

\begin{proof}
  See
\end{proof}

@@

  \item Follows from $!_s A \rightarrow {\bf 1}$, so $s \in W$;
  \item Follows from $!_s A \bullet B \leftrightarrow B \bullet !_s A$;
  \item Follows from $!_s A \bullet B \rightarrow !_s A \bullet B \bullet !_s A$ and similarly for $B \bullet !_s A$.
\end{proof}

@@

Let $Q$ be a syntactic quantale as proposed above and
$\mathcal{I} = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature.

@@

  Let $Q$ be a quantale constructed above and $\Box_1, \dots, \Box_n$ be a family of quantic conuclei on $Q$.
  Then there exist a model $\langle Q, [\![.]\!]\rangle$, such that $[\![A]\!] = \bigvee \{ A \}$, $A \in Fm$.
\end{lemma}

@@

  Let $A$ be a set. Then relational quantale on $A$ is a tuple $\mathcal{Q} = \langle \mathcal{A}, \mathcal{I} \rangle$
  where $\mathcal{A} \subseteq 2^{A \times A}$:

  \begin{itemize}
    \item $\langle \mathcal{A}, \subseteq \rangle$ is a complete semi-lattice;
    \item Multiplication is defined as
      $R \circ S = \{ \langle a, c \rangle \: | \: \exists b \in A, \langle a, b \rangle \in R \text{ and } \langle b, c \rangle \in S\}$
    \item $\langle \mathcal{A}, \circ, \mathcal{I} \rangle$ is a monoid;
    \item For each indexing set $J$, $R \circ \bigvee_{i \in I} S_i = \bigvee_{i \in I} (R \circ S_i)$ and
      $\bigvee_{i \in I} R_i \circ S = \bigvee_{i \in I}(R_i \circ S)$.
  \end{itemize}
\end{defin}

@@

\begin{theorem}
  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
\end{theorem}

>>>>

\theoremstyle{col}
\newtheorem{col}{Corollary}
\usepackage{listings} 		% for source code
\date{}
\author[1,2]{Daniel Rogozin}
\affil[1]{Lomonosov Moscow State University}
\affil[2]{Serokell O\"{U}}
\title{Models of Lambek calculus with subexponentials}

@@

  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash
  \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | ({!_s \mathcal{F}_{\Sigma}})_{s \in
  \Sigma} $
\end{defin}

@@

@@

Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and $\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of
$\mathcal{Q}_1$.

@@

  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$. Let $a_i \in S$ for each $i
  \in I$, so $\bigvee \limits_{i \in I} a_i \in S$, but $f(a_i) \in f(\mathcal{S})$ for any $i \in I$, so $f(\bigvee
  \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} (f (a)) \in f(\mathcal{S})$, so $f(\mathcal{S})$ is closed
  under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
\end{proof}

@@

\begin{lemma}
  $\Box_1 a_1 \cdot \Box_2 a_2 \leq \Box (\Box_1 a_1 \cdot \Box_2 a_2)$, where $\Box_i \leq \Box, i = 1,2$.
\end{lemma}

@@

\begin{defin}
$ $
\begin{enumerate}
  \item An open modality is called central, if for all
  $a, b \in \mathcal{Q}, \Box a \cdot b = b \cdot \Box a$.

@@

  $\begin{array}{lll}
  & b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Right weak square-increase}& \\
  &\Box a \cdot b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Unitality}& \\
  & \Box a \cdot b \cdot e \leq & \\
  & \:\:\:\: \text{Identity}& \\
  &\Box a \cdot b \leq & \\
  & \:\:\:\: \text{Left weak square-increase}& \\
  &\Box a \cdot b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Unitality}& \\
  &e \cdot b \cdot \Box a \leq & \\
  & \:\:\:\: \text{Identity}& \\
  &b \cdot \Box a&
  \end{array}$

@@

  Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale,
  then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
\end{prop}

\begin{proof}
  See Rosenthal.
\end{proof}

@@

\begin{enumerate}
  \item $\Box_z (a) = \bigvee \{ s \in S \: | s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \}$;
  \item $\Box_{\mathds{1}} (a) = \bigvee \{ s \in S \: | s \leq a, s \leq \mathds{1} \}$;
  \item $\Box_{idem} (a) = \bigvee \{ s \in S \: | s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$;
  \item Operations with combinations of conditions above;
\end{enumerate}
\end{prop}

@@

The following conditions hold similarly to \cite{Gurr}:

  \begin{enumerate}
  \item $\bigvee S$ is an ideal;
  \item $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$;
  \item $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$;
  \item Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a unital quantale.
  \end{enumerate}
\end{lemma}

We extend this construction for polymodal case as follows:

@@

\begin{enumerate}
  \item Follows from $!_s A \rightarrow {\bf 1}$, so $s \in W$;
  \item Follows from $!_s A \bullet B \leftrightarrow B \bullet !_s A$;
  \item Follows from $!_s A \bullet B \rightarrow !_s A \bullet B \bullet !_s A$ and similarly for $B \bullet !_s A$.
\end{enumerate}
\end{proof}

@@

Let $\mathcal{Q}$ be a syntactic quantale as proposed above and
$\mathcal{I} = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature.

@@

  Let $Q$ be a quantale constructed above and $(\Box_{s_i})_{s_i \in \Sigma}$ be a family of quantic conuclei on $Q$.
  Then there exist a model $\langle Q, [\![.]\!]\rangle$, such that $[\![A]\!] = \bigvee \{ A \}$, $A \in Fm$.
\end{lemma}

@@

  Let $A$ be a set. Then relational quantale on $A$ is a triple $\mathcal{Q} = \langle \mathcal{A}, \bigvee, \mathcal{I}
  \rangle$ where $\mathcal{A} \subseteq 2^{A \times A}$:

  \begin{itemize}
    \item $\langle \mathcal{A}, \bigvee, \subseteq \rangle$ is a complete semi-lattice;
    \item Multiplication is defined as
      $R \circ S = \{ \langle a, c \rangle \: | \: \exists b \in A, \langle a, b \rangle \in R \text{ and } \langle b, c \rangle \in S\}$
    \item $\langle \mathcal{A}, \circ, \mathcal{I} \rangle$ is a monoid;
    \item For each indexing set $J$, $R \circ \bigvee_{i \in I} S_i = \bigvee_{i \in I} (R \circ S_i)$ and
      $\bigvee_{i \in I} R_i \circ S = \bigvee_{i \in I}(R_i \circ S)$.
  \end{itemize}
\end{defin}

@@

\section{Syntactic concept lattices}

\begin{defin}
  Let $\mathcal{L}$ be a finite alphabet and $L \subseteq \mathcal{L}^{*}$ be a language.

  We define maps $[.]^{\triangleright} : \mathcal{P}(\mathcal{L}^{*}) \to \mathcal{P}(\mathcal{L}^{*} \times \mathcal{L}^{*})$
  and $[.]^{\triangleleft} : \mathcal{P}(\mathcal{L}^{*} \times \mathcal{L}^{*}) \to \mathcal{P}(\mathcal{L}^{*})$ as follows:

  \begin{enumerate}
    \item $M \subseteq \mathcal{L}^{*}$, $M^{\triangleright} = \{ (x, y) \: | \: \forall w \in M, x w y \in L \}$;
    \item $C \subseteq \mathcal{L}^{*} \times \mathcal{L}^{*}$, $C^{\triangleleft} = \{ w \: | \: \forall (x, y) \in C, x w y
    \in L\}$
  \end{enumerate}
\end{defin}

Note that compositions $[.]^{\triangleleft \triangleright}$ and $[.]^{\triangleright \triangleleft}$ form closure operators,
by the way $[.]^{\triangleleft}$ and $[.]^{\triangleright}$ are connected via contravariant Galois connection.

\begin{defin} A syntactic concept is a pair $\langle S, C \rangle$, where $S \subseteq \mathcal{L}^{*}$
  and $C \subseteq \mathcal{L}^{*} \times \mathcal{L}^{*}$, such that $S^{\triangleright} = C$ and $C^{\triangleleft} = S$.
\end{defin}

### 2019-04-07 RModels.tex
updates in notation and defs

\begin{theorem}
  Let $\mathbb{F}$ be a $R$-frame, then $\mathbb{F} \models L$.
\end{theorem}

@@

  \begin{enumerate}
    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.
    Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.

    \item Let $\mathcal{F}_1$ and $\mathcal{F}_2$ be $R$-frames and $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$,
    then $\mathcal{F}_1 \models A$ implies $\mathcal{F}_2 \models A$.
  \end{enumerate}
\end{lemma}

@@

    Let $\mathcal{M}_1 \models A$. Let $c, d \in W_2$. So far as $f$ is onto,
    then there exists $a, b \in W_1$, such that $f(a) = c$ and $f(b) = d$.

@@

    Follows from the previous lemma.
  \end{itemize}
  \item Let $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ and $\mathcal{F}_1 \models A$.

  Let $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$ and $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$, such that
  for all $p \in Tp$,
  $\mathcal{M}_1, \langle a, b \rangle \Vdash p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \Vdash p$.
  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \models A$. Thus, $\mathcal{M}_2 \models A$.
\end{enumerate}
\end{proof}

>>>>

\begin{theorem}
  Let $\mathbb{F}$ be a $R$-frame, then $\mathbb{F} \Vdash L$.
\end{theorem}

@@

  \begin{enumerate}
    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.
    Then $\mathcal{M}_1 \Vdash A$ iff $\mathcal{M}_2 \Vdash A$.

    \item Let $\mathcal{F}_1$ and $\mathcal{F}_2$ be $R$-frames and $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$,
    then $\mathcal{F}_1 \Vdash A$ implies $\mathcal{F}_2 \Vdash A$.
  \end{enumerate}
\end{lemma}

@@

    Let $\mathcal{M}_1 \Vdash A$. Let $c, d \in W_2$. So far as $f$ is onto,
    then there exists $a, b \in W_1$, such that $f(a) = c$ and $f(b) = d$.

@@

    Follows from the previous lemma.
  \end{itemize}
  \item Let $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ and $\mathcal{F}_1 \Vdash A$.

  Let $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$ and $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$, such that
  for all $p \in Tp$,
  $\mathcal{M}_1, \langle a, b \rangle \Vdash p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \Vdash p$.
  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \Vdash A$. Thus, $\mathcal{M}_2 \Vdash A$.
\end{enumerate}
\end{proof}

\begin{defin}
\end{defin}
